---
title: "caribouNT_studyArea"
author: ""
date: "23 March 2022"
output:
  html_document:
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, results = "hold")
```

# Overview

Create study area objects required for running LandR-fireSense simulations for caribou management in the Northwest Territories, Canada.

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("caribouNT_studyArea", "..")
knitr::kable(df_params)
```

# Events

Currently everything happens in a single `init` event.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("caribouNT_studyArea", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("caribouNT_studyArea", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("caribouNT_studyArea", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Initially developed for use with LandR Biomass forest dynamics and fireSense wildfires suites of modules.
